---
# NB - ONLY CHANGE THE LINES WHICH HAVE BEEN HIGHIGHTED WITH COMMENTS 
# TO DO SO - LIKE THIS 

title: "TITLE OF THE STUDY HERE" # CHANGE THIS 
poster_height: "48in"
poster_width: "36in"
font_family: "Rasa"

author:
  - name: "Student Name" # CHANGE THIS 
    affil: 1
    main: true
    email: "student@brunel.ac.uk" # CHANGE THIS 

affiliation:
  - num: 1
    address: "Department of Psychology, Brunel University of London"

primary_colour: "#008080"
secondary_colour: "#0b4545"
accent_colour: "#cc0000"

main_fontfamily: "Special Elite"
main_textcol: "#FFFFFF90"
main_textsize: "170px"
main_findings: "ONE SENTENCE MAIN TAKE AWAY OF YOUR STUDY." # CHANGE THIS 

body_bgcol: "#FFFFFF"
body_textsize: "45px"
body_textcol: "#000000"

title_textsize: "125pt"
author_textsize: "1.17em"
authorextra_textsize: "35px"
affiliation_textsize: "25px"
affiliation_textcol: "#00000060"

caption_textsize: "20pt"
reference_textsize: "20px"

output:
  posterdown::posterdown_betterport:
    self_contained: true
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

# Load required packages
library(tidyverse) 
# INCLUDE ANY OTHER PACAKGES YOU REQUIRE

# load required dats 
mydata <- read_csv("mydata.csv") # WILL BE PROVIDED TO YOU  

```
<br>

 ----- NB EVERYTHING ELSE BELOW CAN BE CHANGED EXPECT FOR THE R SETUP CODE IN EACH
CODE CHUNK - DON'T TOUCH THAT ----------------------------

# Introduction
THREE SENTENCE SUMMARY OF YOUR THE RESEARCH TOPIC, QUESTION AND MOTIVATION. KEEP IT SHORT.  

<br>

# Methods
## Participants and Data
WHO WAS THE PARTICIPANTS, WHAT VARIABLES DID YOU GET IN YOUR DATASET. WHERE THERE NAs?  

## Data Preparation
HOW DID YOU TIDY THE DATA (CHANGE NAMES, HANDLE MISSINGNESS)? HOW DID YOU TRANSFORM THE DATA (MAKE NEW VARIABLES?)

```{r, echo=TRUE, background="#f0f0f0", size="large"}

# THIS CODE CHUNK WILL BE SHOWN IN THE POSTER AS EVIDENCE OF YOUR CODING. MAKE SURE IT IS CLEAR AND WELL COMMENTED. 
# INLCUDE CODE FOR WHAT YOU DID TO TRANSFORM/TIDY THE DATA PRIOR TO ANALYSIS.


```

## Descriptive Statistics
WHAT DESCRIPTIVE STATS DID YOU COMPUTE? WHAT PLOTS DID YOU DECIDE WHERE BEST? 

## Linear Regression 
EXPLAIN THE LINEAR REGRESSION, CHECKING MODEL ASSUMPTIONS HOW YOU REPORTED IT AND ANY VISALUSATION OF IT.
YOU MAY PROVIDE THE EQUATION HERE.

<br>

# Results
ONE SENTENCE ABOUT THE DESCRIPTIVE STATS SUMMARYING THE TABLE BELOW. 

```{r, echo=FALSE}
# Summary table of the  main variables 
```


```{r, echo=FALSE, fig.width=11, fig.height=5}
# PLOTS OF THE DESCRIPTIVE STATS 

```

ONE - TWO SENTENCE SUMMARY OF THE PLOTS AND IMPLICATIONS. 

2-3 SENTENCE SUMMARY OF THE LINEAR REGRESSION RESULTS WITH INTERPRETION FOLLOWING APA GUIDLINES. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Fit linear regression model

# Create a simple coefficients table (you might want to round numbers!) 

# Show the table


```


```{r, echo=FALSE, fig.width=11, fig.height=5, message=FALSE, warning=FALSE}
# PLOT TO VISUALISE THE RELATIONSHIP BETWEEN MAIN VARIABLES TO SUPPORT YOU 
# LINEAR REGRESSION. 

```

USING THE FORMULA ABOVE, TELL US WHAT IS THE PREDICTED VALUE OF THE DEPENDENT VARIABLE FOR THE MEAN OF THE INDEPENDENT VARIABLE

CONFIRM YOU DID THE MODEL ASSUMPTION CHECKS AND IF THERE WERE ISSUES OR NOT. IF SPACE (OPTIONAL) INCLUDE AN PLOT/OUTPUT OF THE ASSUMPTION CHECKS. BUT YOU MIGHT WANT TO FOCUS ON THE ABOVE RESULTS. 

```{r, echo=FALSE, fig.width=11, fig.height=5}
# EG. Q-Q PLOTS 
```
<br>

# Conclusion 

THREE LINE SUMMARY OF YOUR FINDINGS AND IMPLICATIONS 
