---
title: ""
author: ""
date: ""
output:
  pagedown::html_paged:
    self_contained: true
    css:
      - poster_columns.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)

poster_title <- "Children's emotional regulation"
poster_author <- "Abigail E. Page, abigail.page@brunel.ac.uk"
poster_affiliation <- "Department of Psychology, Brunel University of London"

# load required data
df <- read.csv("dev_data.csv")
```

<div class="poster-wrapper"> <div class="poster-header"> <div class="poster-title">`r poster_title`</div> <div class="poster-meta"> <strong>Author:</strong> `r poster_author`<br> <strong>Affiliation:</strong> `r poster_affiliation` 

</div> <div class="main-finding"> Older children show stronger emotional regulation than younger children. 

</div> </div> <div class="poster-columns"> <div class="poster-column"> <div class="panel"> <h2>Introduction</h2>

Children’s ability to regulate emotions improves as they grow, but the pace and patterns of this development vary. This study examines how emotional regulation scores differ across age groups in a sample of children aged 5–12. We expected older children to regulate their emotions better than younger children.
</div> <div class="panel"> <h2>Methods</h2> <h3>Participants and Data</h3>
Data were collected from a sample of children aged 60-150 months, each of whom completed an emotional regulation assessment in an online survey alongside demographic data. The dataset included age in months and an emotional regulation score.

<br>
<h3>Data Preparation</h3>

Age in months was converted into years to make results easier to interpret. The dataset was then cleaned by removing missing values on the key variables.

<br>

```{r, echo=TRUE, background="#f0f0f0", size="large"}

# emotional_regulation is too long name. rename it. 
df <- df %>%
  rename( # function rename 
    emoreg = emotional_regulation) 
# variable now called 'emoreg' 

# mutate the months variable into age 
df <- df %>%
  mutate(age = (months/12)) 
# age is the new variable which is months
# variable divided by 12 

# Check for missing values in key variables
colSums(is.na(df[, c("age", "emoreg")]))

# There are one missing in age and 2 in emoreg
# Remove missing values ONLY for relevant variables

df_clean <- df %>%
  drop_na(age, emoreg)

```

<br>
<h3>Descriptive and Inferential Statistics</h3>

Descriptive statistics were computed for age and emotional regulation and summarised in a table and density plots. A simple linear regression tested whether age predicted emotional regulation. A scatterplot with a fitted regression line and 95% confidence interval was used to visualise the relationship, and a Q-Q plot was used to assess residual normality.

</div> </div> <div class="poster-column"> <div class="panel"> <h2>Descriptive Results</h2>

The dataset included 20 children aged 5–12 years (mean age = 8.25 years, SD = 2.38). Emotional regulation scores ranged from 3.5 to 12.0, with a mean of 8.44 (SD = 2.10).

<br>

```{r, echo=FALSE}
# Summary table of the two main variables
summary <- df_clean %>%
  summarise(
    Mean_Age = mean(age),
    SD_Age = sd(age),
    Mean_ER = mean(emoreg),
    SD_ER = sd(emoreg),
  ) 

knitr::kable(summary, caption = "Summary Statistics for Age and Emotional Regulation")
```



Density plots of the two variables show that age was approximately normally distributed, while emotional regulation scores were slightly positively skewed, with most children scoring between 6 and 10.

<br>
**Figure 1. Density plot for Age**

```{r, echo=FALSE, fig.width=13, fig.height=13}
# ⃣ Density plot of Age
ggplot(df_clean, aes(x = age)) +
  geom_density(fill = "#008080", alpha = 0.7) +
  labs(x = "Age (years)", y = "Density", title = "") +
  theme_minimal(base_size = 26)
```

<br>
**Figure 2. Density plot for emotional regulation**

```{r, echo=FALSE, fig.width=13, fig.height=13}
# ⃣ Density plot of Emotional Regulation
ggplot(df_clean, aes(x = emoreg)) +
  geom_density(fill = "#cc0000", alpha = 0.7) +
  labs(x = "Emotional regulation score", y = "Density", title = "") +
  theme_minimal(base_size = 26)
```


</div> </div> <div class="poster-column"> <div class="panel"> <h2>Regression Results</h2>

A simple linear regression was conducted to examine whether age predicted emotional regulation in children aged 5-12. The model was significant, <em>F</em>(1, 18) = 28.71, <em>p</em> < .001, and explained a substantial proportion of the variance in emotional regulation, <em>R</em><sup>2</sup> = 0.61. Age was a significant positive predictor of emotional regulation, <em>B</em> = 0.80, <em>SE</em> = 0.15, <em>p</em> < .001, indicating that older children tended to have higher emotional regulation scores.

```{r, echo=FALSE}
# Fit linear regression model
model <- lm(emoreg ~ age, data = df_clean)

# Create a simple coefficients table and round numbers
coef_table <- as.data.frame(round(summary(model)$coefficients, 3))

# Show the table with a title
knitr::kable(coef_table, caption = "Linear regression model results")

```

<br>
**Figure 3. Scatter plot for the relationship between age and emotional regulation**

```{r, echo=FALSE, fig.width=13, fig.height=10, message=FALSE, warning=FALSE}
# Scatter plot of Age vs Emotional Regulation
ggplot(df_clean, aes(x = age, y = emoreg)) +
  geom_point(color = "#0b4545", size = 3, alpha = 0.7) +
  geom_smooth(method = "lm", color = "#008080", se = TRUE) +
  labs(x = "Age (years)", y = "Emotional Regulation Score",
       title = "") +
  theme_minimal(base_size = 26)
```

Residuals were checked for normality and Q-Q plots showed approximate normality.

<br>

</div> <div class="panel"> <h2>Conclusion</h2>
This study demonstrates that emotional regulation improves with age in children aged 5-12. Older children showed stronger self-regulation than younger children, consistent with typical developmental trends. These findings highlight the importance of supporting emotional skills in early childhood to promote healthy development.


