---
title: "wide-to-long excess "
output: html_notebook
---


## Wide and long data

Real research data rarely arrive in the “perfect” format for analysis. The same information can be organised in at least two fundamentally different ways:

  1) **Wide format** – one row per participant, repeated measures stored in multiple columns
  2) **Long format** – one row per observation, with a variable that tells you which condition or time point it belongs to. 

Neither format is “right” or “wrong”. They simply serve different purposes. You will need to work out what format your need your data in deepening on your purpose! 

### Wide data 

In *wide data* each person appears in ONLY one row, and each observation or data point collected on them has a seperate column. For instance, if you were measuring anxiety at three separate time points in the same participant it would like this: 

| id | anxiety_t1 | anxiety_t2 | anxiety_t3 |
|----|------------|------------|------------|
| 1  | 12         | 10         | 8          |
| 2  | 15         | 14         | 13         |

It's called wide data because as you collect more and more data on a participant you can imagine the dataset getting wider and wider as more columns are filled up! 

This format is: 

  - easy for us to read as people 
  - similar to how online surveys (Like Qualtrics) kick out data when you have asked participants a bunch of questions 
  - convenient for commuting summary statistics (e.g. mean anxiety score)

### Long data 

In long data, each measurement will get its own row, so participants will be spread across many rows - making your data very long: 

| id | time | anxiety |
|----|------|---------|
| 1  | t1   | 12      |
| 1  | t2   | 10      |
| 1  | t3   | 8       |
| 2  | t1   | 15      |
| 2  | t2   | 14      |
| 2  | t3   | 13      |

This structure is harder for us to read but is often expected in repeated measures models. For within-subject designs, where the same participant is measured more than once (paired t-test, repeated-measures ANOVA and linear mixed models) the analysis needs to kmnow 1) which row belongs to the same person and 2) which condition/time each score represents. This only is clear in the long format. 

What this means is that when you have wide data, you might need to **pivot** it to a long format. 

### Converting wide to long with `pivot_longer()` 

Imagine we collected three height measurements per student as they grow over time: 

```{r wide df}

# make a wide dataframe:  

df_wide <- data.frame(
  id = 1:3, # 1 participants 
  h1 = c(154, 159, 167), # first height for each participant  
  h2 = c(165, 162, 179), # second height for each participant
  h3 = c(171, 163, 181)  # third height for each participant
)

# view the dataframe 
df_wide

```

So to make it long we need to pivot the table so you have one column which is `id`, one column as `height` and a new column which is `time` which is when each of these height measures are taken. 

```{r pivot longer}

# pivot df longer 

df_long <- df_wide %>% # renames df based on the df_wide 
  pivot_longer(
    cols = c(h1, h2, h3), # these are the columns to reduce to one 
    names_to = "time", # this takes the names of the original columns into 
    # the new variable `time`  
    values_to = "height" # the values of h1-h3 are in the new variable 'height
  )

# view the new dataset
df_long

```

Now we have:
  
  - one column saying which height measure
  - one column containing the actual values

> **Question 7.1**: how many rows did the df_wide have? How many rows does the df_long have? 

### Pivoting long to wide with `pivot_wider()` 

Sometimes we need to do the opposite and change it from long format to wide. We can change the new df_long back to df_wide if we like: 

```{r long df to wide}

# pivot wider 
df_wide2 <- df_long %>% # rename the df df_wide2 not to overwrite 
  pivot_wider( # function 
    names_from = time, # the variables labelled from 'time' column 
    values_from = height # values from the height column 
  )

# view df to confirm 
df_wide2


```

Now it is back to where it was originally. Something like this would be useful if your, like we did above, computing a total GAD-7 score from gad1-gad7. 

### Activity 7.1: pivoting the tidyverse df

Going back to the dataframe we were using for the tidyverse verbs, you will remember we had three variables measuring height. To pivot this from wide to long, follow these steps: 

  1) **Step 1**: use `pivot_wider()` on `df` and rename to `dflong` 
  2) **Step 2**: Name columns “measurement” in `names_to` 
  3) **Step 3**: Pull the values of height into the `heights` column with `values_to` 
  4) **Step 4**: View the new dataset and answer the following questions 
  
> **Question 4.7**: how many rows does this new long dataset have? 

> **Question 4.8**: for the other variables (e.g. total, gender) how are they now recorded for each paritcipant? 

  5) **Step 5**: convert this back to from long to wide again and check it matches the original structure. 
  

Key take-aways: 

  - Wide = one row per person
  - Long = one row per observation
  - Repeated measures almost always require long
  - `pivot_longer()` and `pivot_wider()` let you move flexibly between them
  - Analyes might require you to switch format depending on task
